Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-09-13 GWLDCII.tex
made the small changes I was asked to

@@

The next few lemmas describe how the Grassmann necklaces (Lemma \ref{lem I}) and the Le diagrams (Lemmas \ref{lem shape} to Lemma \ref{lem other k}) of Wilson loop diagrams of this type are related to the corresponding Wilson loop diagram with propagator $p$ removed. \sanote{rephrased, still clear?}

>>>>

\begin{rmk}\label{rmk cyclic}
  Before the proof, let us observe that one of the main ways that the above lemma will be used is in observations like the following.  Suppose $p=(i,j)$ is a propagator and $I_{j+1}(p) = j+1$.  Consider $I_{j+2}(p)$.  Since $j+1$ is the last vertex in the $j+2$ order, $p$ can not contribute $j+1$ to $I_{j+2}$.  But the the fact that the invervals of the lemma are nonempty and occur in their cyclic order implies that $I_{j+2}(p)=i$.  More generally, whenever we know that a propagator stops contributing a particular vertex, then we know that it must contribute its cyclically next vertex.  This little observation is surprisingly useful, to the point that the details which appear in the proof of Lemma~\ref{vertex cyclic int lem} are never needed again, the mere fact of non-empty intervals in the correct order suffices.
\end{rmk}

Now we proceed to the proof of Lemma~\ref{vertex cyclic int lem}.

@@

With the above restrictions in place, the next few lemmas describe how the Grassmann necklaces (Lemma \ref{lem I}) and the Le diagrams (Lemmas \ref{lem shape} to Lemma \ref{lem other k}) change upon the removal of $p$ from the Wilson loop diagram.  This gives us the inductive lever we need to prove the main theorem (Theorem \ref{thm dim}).
